The \dealii Library, Version 9.6

### 2024-08-16 9.6/paper.tex
Fix author affiliations

\author[16]{Bruno~Turcksin}

\author[17]{David Wells}
\affil[17]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[17]{Vladimir Yushutin}
\affil[17]{Department of Mathematics, University of Tennessee at Knoxville,
	 Knoxville TN 37996-1320, USA
{\texttt{vyushuti@utk.edu}}}

>>>>

\author[2]{Bruno~Turcksin}

\author[16]{David Wells}
\affil[16]{Department of Mathematics, University of North Carolina,
  Chapel Hill, NC 27516, USA.
  {\texttt{drwells@email.unc.edu}}}

\author[17,8]{Vladimir Yushutin}
\affil[17]{Department of Mathematics, University of Tennessee at Knoxville,
	 Knoxville TN 37996-1320, USA.
{\texttt{vyushuti@utk.edu}}}
